Adaptative neigbouring methods applied to telephonic base stations

### 2024-08-19 article.tex
Légère correction de mise en page

\begin{itemize}
    \item \emph{$\epsilon$} : A distance threshold under which two points are considered close enough to be considered neighbours;   
    \item \emph{$n_{\text{min}}$} : The shortest number of neigbours a points needs to have to be considered as a core point of a cluster.

@@

The clusters will then "grow" from the core points by attaching all points close from less than \emph{$epsilon$} than a point of the said 
cluster.

@@

\subsubsection{\acrshort{hdbscan}}
This method, introduced here \cite{10.1007/978-3-642-37456-2_14} is a variation of the \acrshort{dbscan} method. It consists
in selecting the best clusters after testing their persistence by making the $\epsilon$ parameter vary. It's main particularity
is that it allows to detect clusters of different densities.

@@

For each base station $i$, the mean distance to its three nearest neighbours is calculated (we will call this value $\gamma_i$, in 
$\unit{km}$). According to the value of $\gamma_i$, the base station can either be classified as part of one of the categroies of 
Table~\ref{table:crit_summary} (very low value for city center, slighlty higher value for urban area,\dots).

>>>>

\begin{itemize}
    \item \emph{$\varepsilon$} : A distance threshold under which two points are considered close enough to be considered neighbours;   
    \item \emph{$n_{\text{min}}$} : The shortest number of neigbours a points needs to have to be considered as a core point of a cluster.

@@

The clusters will then \og grow\fg{} from the core points by attaching all points close from less than \emph{$\varepsilon$} than a point of the said 
cluster.

@@

\subsubsection{\acrshort{hdbscan}}
This method, introduced here \cite{10.1007/978-3-642-37456-2_14} is a variation of the \acrshort{dbscan} method. It consists
in selecting the best clusters after testing their persistence by making the $\varepsilon$ parameter vary. It's main particularity
is that it allows to detect clusters of different densities.

@@

For each base station $i$, the mean distance to its three nearest neighbours is calculated (we will call this value $\gamma_i$, in 
$\unit{km}$). According to the value of $\gamma_i$, the base station can either be classified as part of one of the categroies of 
Table~\ref{table:crit_summary} (very low value for city center, slighlty higher value for urban area, \dots).
